An Overview of Distributed Version Control Systems

### 2010-06-26 laarsample.tex
Movido un párrafo a la introducción que es donde correspondía

@@

For reference, in this paper we'll base our explanations on Git but for most features there 
are no big differences between most of these DVCS, especially between Git and Mercurial which are 
largely similar, with most commands having the same names in both tools.

>>>>

This paper bases its explanations on Git but for most features there 
are no big differences between most of these DVCS, especially between Git and Mercurial which are 
largely similar, with most commands having the same names in both tools.

@@
